Death by Dropdown?<br>Engineer Insightful Shiny Apps<br>with Behavioral Science

### 2025-09-11 conference-materials/2025_posit-conf/draft.qmd
Remove legacy files and update conference materials
- Deleted research artifacts (`bid-framework.qmd`, `.rds` files, `.bib`) no longer required.
- Removed placeholder `app.R` example in the Shiny dashboard directory.
- Updated README to reference a relative image path for improved portability.
- Changed the conference draft date in `.qmd` and `.html` files from September 17 to September 7, 2025.

---
title: "Death by Dropdown?<br>Engineer Insightful Shiny Apps<br>with Behavioral Science"
author: "Jeremy Winget, PhD"
date: "September 17, 2025"
date-format: "MMMM D, YYYY"
execute:
  echo: true
  eval: true
format:
  revealjs:
    code-block-background: true
    highlight-style: github
    slide-number: false
    transition: fade
    auto-animate: true
    width: 1600
    height: 900
    footer: "posit::conf(2025) | jrwinget\\.com"
    title-slide-attributes:
      data-background-image: "img/posit-conf.png"
      data-background-position: "top left"
      data-background-repeat: "no-repeat"
      data-background-color: "#213d4f"
      data-background-opacity: "0.25"
      data-background-size: "45%"
---

>>>>

---
title: "Death by Dropdown?<br>Engineer Insightful Shiny Apps<br>with Behavioral Science"
author: "Jeremy Winget, PhD"
date: "2025-09-07"
date-format: "MMMM D, YYYY"
execute:
  echo: true
  eval: true
format:
  revealjs:
    code-block-background: true
    highlight-style: github
    slide-number: false
    transition: fade
    auto-animate: true
    width: 1600
    height: 900
    footer: "posit::conf(2025) | jrwinget\\.com"
    title-slide-attributes:
      data-background-image: "img/posit-conf.png"
      data-background-position: "top left"
      data-background-repeat: "no-repeat"
      data-background-color: "#213d4f"
      data-background-opacity: "0.25"
      data-background-size: "45%"
---
